---
title: 'Exercise 3: R Markdown Presentation Slides'
author: Tracy Wang
date: September 2019
autosize: true
output: 
  ioslides_presentation:
    incremental: true
    template: quarterly-report.html

---


# Slides!

This will be a presentation version of the Orange dataset exploration presented in Exercise 2.

## Orange

Orange is a dataset about the growth of five orange trees. This is a record of their trunk circumferences (in cm) at certain ages (in days).

The headers for the Orange dataset, as determined through the names() function, are:

```{r load, warning=FALSE, echo=FALSE}
library(tibble)
library(gapminder)
library(DT)

names(Orange)
```

## {.smaller}

The full dataset, presented as a tibble:

```{r tibble, warning=FALSE, echo=FALSE}
datatable(as_tibble(Orange))
```

## Summary {.smaller}

Here is a summary of the Orange dataset using the summary() function:

```{r summary, warning=FALSE, echo=FALSE}
library(knitr)
kable(summary(Orange), align='c', caption="Summary of Orange dataset columns")
```


## Plot

And here is a plot of tree circumference versus age:

```{r plot, warning=FALSE, echo=FALSE}
plot(x=Orange[,2], y=Orange[,3], xlab="Age (days)", ylab="Circumference (cm)", main="Tree size with age", type='p')
abline(lm(circumference~age, data=Orange), col='red')
```

## Observations | some (very) brief notes 

- Obviously we cannot conclude this is a linear relationship. 
- However, the goal here was simply to add a trendline, and that was a success!

# The end

